---
title: "Introduction to ecce"
author: "[Xinyuan Chu](https://cxy.rbind.io)"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    number_sections: no
    toc: yes
classoption: "hyperref,"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Introduction to ecce}
  %\VignetteEncoding{UTF-8}
---

## Introduction

The goal of ecce is to make it easy to translate English words into Chinese, or translate Chinese words into English. It support pipe functions ` %>% ` to manipulate data.

```{r, eval = FALSE}
# Install development version from GitLab
remotes::install_git("https://gitlab.com/chuxinyuan/ecce.git")
```

## Basic usage

### Translate a single words

```{r, eval = FALSE}
# Example-1
x1 <- "苹果"
translate(x1)

# Example-2
x2 <- "apple"
translate(x2)
```

### Translate a vector of words

```{r, eval = FALSE}
# Example-3
x3 <- c("苹果", "香蕉", "梨子", "我爱你")
translate(x3)

# Example-4
x4 <- c("apple", "banana", "pear", "I love you")
translate(x4)
```

## Get more useful translation information 

```{r, eval = FALSE}
# Example-5
x5 <- "苹果"
translate_full(x5)

# Example-6
x6 <- "apple"
translate_full(x6)
```

This function `translate_full()` also support pass into a vector which consists of Chinese or English words. But the form of output is not elegant enough.

## Browse translate results in website

```{r, eval = FALSE}
# Example-7
x7 <- "苹果"
translate_view(x7)

# Example-8
x8 <- "apple"
translate_view(x8)
```

In the same way, this function also support pass into a vector.

## Manipulate data with pipe

```{r eval = FALSE}
library(dplyr)
love <- c("father", "mother", "I love U")
love %>%  
  translate() %>% 
  paste0(., collapse = "")
```

## Code sources and improvements

ecce package is based on [RYoudaoTranslate](https://CRAN.R-project.org/package=RYoudaoTranslate)(Ke-Hao Wu, 2014), which provides function to translate English words into Chinese. also provides interface to Youdao translation open API for R user. But this software is not very friendly to use, which can't support translate Chinese words into English, I have made some improvements on the basis of this software.

## References

Ke-Hao Wu (2014). RYoudaoTranslate: R package provide functions to translate English words into Chinese. R package version 1.0. https://CRAN.R-project.org/package=RYoudaoTranslate









